Data analysis for employee cluster descriptive statistics

### 2023-08-22 04. Analysis/scripts/03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Update 03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Adding summaries for GSA regions, position categories and grades.

@@

```{r}
d %>% 
  group_by(.cluster_2) %>% 
  count(short_id) %>% 
  ungroup() %>% 
  left_join(
    d %>% 
  count(.cluster_2, name = "tot")
  ) %>% 
  mutate(
    prop = n/tot
  ) %>% 
  ggplot(aes(x = .cluster_2, y =  prop,fill = .cluster_2)) +
  geom_col(position = "dodge")  +
  facet_wrap(facets = vars(short_id), scales = "free_y")
```

@@

@@

@@

Disproportionately from FAS, GSA IT, OCFO, OGP, and OHRM, and fewer in PBS

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

```{r}
d %>% 
  group_by(.cluster_5) %>% 
  skim(exit_employment,
       multiple_supervisors) 
```

>>>>

#### GSA Region

@@

```{r}
level_10 <- 
  d %>% 
  count(gsa_region) %>% 
  arrange(desc(n)) %>% 
  slice(10) %>% 
  pull(n)

d %>%
  # mutate(gsa_region = fct_lump_min(gsa_region, min = level_10)) %>%
  group_by(.cluster_2) %>%
  count(gsa_region) %>%
  ungroup() %>%
  left_join(d %>%
              count(.cluster_2, name = "tot")) %>%
  mutate(prop = n / tot) %>%
  ggplot(aes(x = .cluster_2, y =  prop, fill = .cluster_2)) +
  geom_col(position = "dodge")  +
  facet_wrap(facets = vars(gsa_region), scales = "free_y")
```

@@

```{r}
level_10 <- 
  d %>% 
  count(gsa_region) %>% 
  arrange(desc(n)) %>% 
  slice(10) %>% 
  pull(n)

d %>%
  # mutate(gsa_region = fct_lump_min(gsa_region, min = level_10)) %>%
  group_by(.cluster_5) %>%
  count(gsa_region) %>%
  ungroup() %>%
  left_join(d %>%
              count(.cluster_5, name = "tot")) %>%
  mutate(prop = n / tot) %>%
  ggplot(aes(x = .cluster_5, y =  prop, fill = .cluster_5)) +
  geom_col(position = "dodge")  +
  facet_wrap(facets = vars(gsa_region), scales = "free_y")
```

#### Position category

```{r}
level_10 <- 
  d %>% 
  count(position_category_description) %>% 
  arrange(desc(n)) %>% 
  slice(10) %>% 
  pull(n)

d %>%
  # mutate(position_category_description = fct_lump_min(position_category_description, min = level_10)) %>%
  group_by(.cluster_2) %>%
  count(position_category_description) %>%
  ungroup() %>%
  left_join(d %>%
              count(.cluster_2, name = "tot")) %>%
  mutate(prop = n / tot) %>%
  ggplot(aes(x = .cluster_2, y =  prop, fill = .cluster_2)) +
  geom_col(position = "dodge")  +
  facet_wrap(facets = vars(position_category_description), scales = "free_y")
```

```{r}
level_10 <- 
  d %>% 
  count(position_category_description) %>% 
  arrange(desc(n)) %>% 
  slice(10) %>% 
  pull(n)

d %>%
  # mutate(position_category_description = fct_lump_min(position_category_description, min = level_10)) %>%
  group_by(.cluster_5) %>%
  count(position_category_description) %>%
  ungroup() %>%
  left_join(d %>%
              count(.cluster_5, name = "tot")) %>%
  mutate(prop = n / tot) %>%
  ggplot(aes(x = .cluster_5, y =  prop, fill = .cluster_5)) +
  geom_col(position = "dodge")  +
  facet_wrap(facets = vars(position_category_description), scales = "free_y")
```

#### Position category

```{r}
level_10 <- 
  d %>% 
  count(grade) %>% 
  arrange(desc(n)) %>% 
  slice(10) %>% 
  pull(n)

d %>%
  mutate(grade = fct_lump_min(grade, min = level_10)) %>%
  group_by(.cluster_2) %>%
  count(grade) %>%
  ungroup() %>%
  left_join(d %>%
              count(.cluster_2, name = "tot")) %>%
  mutate(prop = n / tot) %>%
  ggplot(aes(x = .cluster_2, y =  prop, fill = .cluster_2)) +
  geom_col(position = "dodge")  +
  facet_wrap(facets = vars(grade), scales = "free_y")
```

```{r}
level_10 <- 
  d %>% 
  count(grade) %>% 
  arrange(desc(n)) %>% 
  slice(10) %>% 
  pull(n)

d %>%
  mutate(grade = fct_lump_min(grade, min = level_10)) %>%
  group_by(.cluster_5) %>%
  count(grade) %>%
  ungroup() %>%
  left_join(d %>%
              count(.cluster_5, name = "tot")) %>%
  mutate(prop = n / tot) %>%
  ggplot(aes(x = .cluster_5, y =  prop, fill = .cluster_5)) +
  geom_col(position = "dodge")  +
  facet_wrap(facets = vars(grade), scales = "free_y")
```

@@

Position categories tend to be Offsite, Onsite Flexible, and Position Has Changed. A very small proportion of Onsite Required.

@@

Disproportionately from FAS, GSA IT, OCFO, OGP, and OHRM, and fewer in PBS.

Disproportionately in Region 0.

@@

Position categories tend to be Onsite Required. All (Missing) and most are in this cluster.

@@

Disproportionately in all regions apart from 0.

@@

Position categories tend to be Offsite and Position Has Changed. A small proportion of Onsite Required.

@@

Disproportionately in Region 0 and Region 2.

@@

Disproportionately in Region 0.

@@

Position categories tend to be Onsite Flexible.

@@

Disproportionately in Region 1, Region 4, Region 5, Region 8, Region 9, and Region 10.

@@

Position categories tend to be Onsite Required.

@@

Disproportionately in Region 1, Region 2, Region 3, Region 6, Region 7, Region 8, Region 9, Region 10, and Region 11. Very low proportion in Region 0.

@@

Appear across all position categories and make up all of those that are (Missing).

@@

Fairly even dispersion across regions.
